---
format: html
editor: visual
execute:
  echo: false
  warning: false
  message: false
---

# Analysis - Clusters over Time

```{r}
library(tidyverse)
library(arrow)
library(skimr)
library(zoo)
library(knitr)
library(ggridges)
library(patchwork)
library(gifski)
library(gganimate)
library(rstatix)
library(coin)
library(nnet)
library(kableExtra)
library(scales)
library(reticulate)

#setwd("/Users/samcooper/Documents/GitHub/project-writeup-graham-and-sam/") x

qual_pca_nute = read_parquet("shared_data/cluster_pca_map_5_clusters_no_alcohol_nutrient_household_nutrient_per_total_cal_234_inits.parquet")


gor_to_ihme = c(
  "1"  = "North East England",
  "2"  = "North West England",
  "4"  = "Yorkshire and the Humber",
  "5"  = "East Midlands",
  "6"  = "West Midlands",
  "7"  = "East of England",
  "8"  = "Greater London",
  "9"  = "South East England",
  "10" = "South West England",
  "11" = "Wales",
  "12" = "Scotland",
  "13" = "Northern Ireland")



qual_pca_nute = qual_pca_nute %>%
  mutate(
    ihme_region = gor_to_ihme[as.character(gor)])


```

```{r}
# -------------------------------------------------------------------
# >>> SET YOUR INPUT VARIABLES HERE <
# -------------------------------------------------------------------

data_source   = qual_pca_nute        # dataset with hhno, styr, gor, cluster, PC1_score, PC2_score, PC3_score
cluster_col   = "cluster"       # fixed column name in this dataset # used for stacked bar, gif and 
label_name    = "Nutrients"          # — used in titles/filenames # used in all
analysis_type = "Composition"   # used in all
year_col      = "styr"  # used in all
value_cols    = c("PC1_score", "PC2_score")   # loop through PC1 and PC2 # needed for ridge/boxplot
region_col    = "ihme_gor"  # part of the uk # needed for by region plots

```

### Composition Clusters with Bar Graphs and Line Plots

These visualizations detail the change in proportion of each nutrient cluster over time. They demonstrate a slight decrease for cluster 0 from around 25% to 15%. Cluster 1 was relatively stable at around 3%. Cluster 2 showed an increase in proportion from around 3% to 40% with a relatively steep slope. Cluster 3 hobbled around the 20% proportion area, starting a few points above and then ending at a value right around 15%. Lastly, we saw cluster 4 start as the highest proportion, nearly 50% and slowly reduce to 30%. This informs us, as time continued, the trends mapped to cluster 2 becoming more prevalent as 0, 3, and 4 fell. This initial model motivated statistical checks to be ran to ensure the changes in proportion over timer (1974-2000) were statistically significant and not simply attributed to random noise.

```{r}
#| label: fig-R-stacked-bar-and-line
#| fig-cap: "Nutrient cluster proportions over time as stacked bar plot."

## Composition fg 17, then nute, the corresponding dataset will need to be switched

#save_dir = "output_plots"
#dir.create(save_dir, showWarnings = FALSE, recursive = TRUE)

# -------------------------------------------------------------------
# 1. Prep data
# -------------------------------------------------------------------

cluster_data1 = data_source %>%
  select(hhno, all_of(year_col), all_of(cluster_col)) %>%
  filter(!is.na(.data[[cluster_col]]))

cluster_props1 = cluster_data1 %>%
  group_by(.data[[year_col]], .data[[cluster_col]]) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(.data[[year_col]]) %>%
  mutate(
    total = sum(n),
    proportion = n / total
  ) %>%
  ungroup() %>%
  arrange(.data[[year_col]], .data[[cluster_col]])

#print(kable(cluster_props1, digits = 3))


# -------------------------------------------------------------------
# 2. Stacked bar chart — cluster proportions by year
# -------------------------------------------------------------------

p_trend = ggplot(
  cluster_props1,
  aes(x = factor(.data[[year_col]]), y = proportion, fill = factor(.data[[cluster_col]]))
) +
  geom_col(position = "stack", color = "white") +
  labs(
    title = paste0(label_name, " Cluster Proportions (", analysis_type, ") by Year"),
    x = "Survey Year",
    y = "Proportion of Households",
    fill = paste0(label_name, " Cluster")
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

print(p_trend)
#ggsave(
 # file.path(save_dir, paste0(label_name, "_", tolower(analysis_type), "_stacked_bar.png")),
  #p_trend, width = 9, height = 5.5, dpi = 150)






```

```{r}
#| label: fig-R--line
#| fig-cap: "Nutrient cluster proportions over time as line plot."

cluster_props1 = data_source %>%
  filter(!is.na(.data[[cluster_col]])) %>%
  group_by(.data[[year_col]], .data[[cluster_col]]) %>%
  summarise(
    n = n_distinct(hhno),
    .groups = "drop"
  ) %>%
  group_by(.data[[year_col]]) %>%
  mutate(
    total_n = sum(n),
    proportion = n / total_n,
    se = sqrt(proportion * (1 - proportion) / total_n),
    lower = pmax(0, proportion - 1.96 * se),
    upper = pmin(1, proportion + 1.96 * se)
  ) %>%
  ungroup()

p_trend_line = ggplot(
  cluster_props1,
  aes(
    x = .data[[year_col]],
    y = proportion,
    color = factor(.data[[cluster_col]])
  )
) +

  # Recession period around 1992
  annotate(
    "rect",
    xmin = 1991,
    xmax = 1992,
    ymin = -Inf,
    ymax = Inf,
    fill = "grey60",
    alpha = 0.15
  ) +

  annotate(
    "text",
    x = 1992,
    y = Inf,
    label = "Recession",
    vjust = 1.5,
    color = "grey35",
    fontface = "bold",
    size = 3.5
  ) +

  # Cluster trend lines
  geom_line(linewidth = 0.9) +

  # Nutrient cluster colors
  scale_color_manual(
    values = c(
      "0" = "#E69F00",
      "1" = "#56B4E9",
      "2" = "#009E73",
      "3" = "#0072B2",
      "4" = "#CC79A7"
    )
  ) +

  # Axes
  scale_x_continuous(
    breaks = seq(1974, 2020, by = 2),
    expand = expansion(mult = c(0.015, 0.015))
  ) +

  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1),
    expand = expansion(mult = c(0.01, 0.04))
  ) +

  # Labels
  labs(
    title = "Nutrient Cluster Proportions by Survey Year",
    x = "Survey Year",
    y = "Households (%)",
    color = "Nutrient Cluster"
  ) +

  # Match disease graph styling
  theme_bw(base_size = 12) +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    legend.key = element_blank(),
    legend.key.width = unit(0.9, "cm"),
    legend.background = element_rect(
      color = "grey75",
      linewidth = 0.3
    ),
    legend.text = element_text(size = 9),

    panel.grid = element_blank(),
    panel.border = element_rect(
      color = "black",
      fill = NA,
      linewidth = 0.6
    ),

    axis.title = element_text(
      face = "plain",
      size = 10,
      color = "grey30"
    ),
    axis.text = element_text(
      size = 9,
      color = "grey20"
    ),
    axis.text.x = element_text(
  angle = 45,
  hjust = 1,
  size = 8,
  color = "grey20"
),
    plot.title = element_text(
      face = "bold",
      size = 16,
      hjust = 0,
      color = "grey20"
    ),
    plot.title.position = "plot"
  )

print(p_trend_line)
```

### Disease Line Plot (Rename)

```{r}
disease = read_csv("shared_data/IHME-GBD_SEV_metabolic_regions.csv")

uk_label = "United Kingdom"

if (uk_label %in% unique(disease$location)) {

  df_metabolic_uk = disease %>%
    filter(location == uk_label, metric == "Rate")

} else {

  df_metabolic_uk = disease %>%
    filter(location != "Northern Ireland", metric == "Rate") %>%
    group_by(rei, year, metric) %>%
    summarise(
      val   = mean(val, na.rm = TRUE),
      upper = mean(upper, na.rm = TRUE),
      lower = mean(lower, na.rm = TRUE),
      .groups = "drop"
    )

}

# ------------------------------------------------------------
# 5-year moving average (now one row per rei/year, so no more zigzag)
# ------------------------------------------------------------
df_metabolic_5yr = df_metabolic_uk %>%
  arrange(rei, year) %>%
  group_by(rei) %>%
  mutate(
    val_ma5   = zoo::rollmean(val,   k = 5, fill = NA, align = "center"),
    upper_ma5 = zoo::rollmean(upper, k = 5, fill = NA, align = "center"),
    lower_ma5 = zoo::rollmean(lower, k = 5, fill = NA, align = "center")
  ) %>%
  ungroup()

# ------------------------------------------------------------
# Filter for plotting
# ------------------------------------------------------------
df_metabolic_plot = df_metabolic_5yr %>%
  filter(
    year >= 1990,
    year <= 2020
  )

# ------------------------------------------------------------
# Shrink the ribbon width (band stays centered on val_ma5)
# ------------------------------------------------------------

ribbon_shrink = 0.5

df_metabolic_plot = df_metabolic_plot %>%
  mutate(
    upper_ma5 = val_ma5 + (upper_ma5 - val_ma5) * ribbon_shrink,
    lower_ma5 = val_ma5 - (val_ma5 - lower_ma5) * ribbon_shrink
  )

# ------------------------------------------------------------
# Colors
# ------------------------------------------------------------
disease_colors = c(
  "High LDL cholesterol"         = "#D62728",
  "High body-mass index"         = "#6A3D9A",
  "High fasting plasma glucose"  = "#8C564B",
  "High systolic blood pressure" = "#17BECF",
  "Kidney dysfunction"           = "#BCBD22",
  "Low bone mineral density"     = "#E7298A",
  "Metabolic risks"              = "#7F7F7F"
)

# ------------------------------------------------------------
# Plot
# ------------------------------------------------------------
p_metabolic = ggplot(
  df_metabolic_plot,
  aes(
    x = year,
    y = val_ma5,
    color = rei,
    fill = rei
  )
) +
  geom_ribbon(
    aes(
      ymin = lower_ma5,
      ymax = upper_ma5
    ),
    alpha = 0.18,
    color = NA
  ) +
  geom_line(linewidth = 0.9) +

  scale_color_manual(values = disease_colors) +
  scale_fill_manual(
    values = disease_colors,
    guide = "none"
  ) +

  scale_x_continuous(
    breaks = seq(1992, 2020, by = 4),
    expand = expansion(mult = c(0.015, 0.015))
  ) +
  scale_y_continuous(
    breaks = seq(0, 70, by = 10),
    expand = expansion(mult = c(0.01, 0.04))
  ) +

  labs(
    title = "Rates of Metabolic Syndrome Related Chronic Disease Symptoms in\nthe UK from 1990 to 2020",
    x = "year",
    y = "val",
    color = NULL
  ) +

  theme_bw(base_size = 12) +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    legend.key = element_blank(),
    legend.key.width = unit(0.9, "cm"),
    legend.background = element_rect(color = "grey75", linewidth = 0.3),
    legend.text = element_text(size = 9),

    panel.grid = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.6),

    axis.title = element_text(face = "plain", size = 10, color = "grey30"),
    axis.text = element_text(size = 9, color = "grey20"),

    plot.title = element_text(face = "bold", size = 16, hjust = 0, color = "grey20"),
    plot.title.position = "plot"
  )

print(p_metabolic)


```

```{r}

## GIF of by year nute cluster proportion sizes

 # save_dir = "output_plots"
 # dir.create(save_dir, showWarnings = FALSE, recursive = TRUE)

# # -------------------------------------------------------------------
# # 1. Prep data
# # -------------------------------------------------------------------

 # cluster_data = data_source %>%
 #   select(hhno, all_of(year_col), all_of(cluster_col)) %>%
 #   filter(!is.na(.data[[cluster_col]]))
 # 
 # cluster_props = cluster_data %>%
 #   group_by(.data[[year_col]], .data[[cluster_col]]) %>%
 #   summarise(n = n(), .groups = "drop") %>%
 #   group_by(.data[[year_col]]) %>%
 #   mutate(
 #     total = sum(n),
 #     proportion = n / total
 #   ) %>%
 #  ungroup() %>%
 #   arrange(.data[[year_col]], .data[[cluster_col]])
 # 
 # print(kable(cluster_props, digits = 3))


# -------------------------------------------------------------------
# 2. Static bar plot per year (loop, non-animated reference frames)
# -------------------------------------------------------------------

 # years = sort(unique(cluster_props[[year_col]]))
 # y_max = max(cluster_props$proportion, na.rm = TRUE)
 # 
 # for (y in years) {
 # 
 #   year_data = cluster_props %>% filter(.data[[year_col]] == y)
 # 
 #   p_year = ggplot(year_data, aes(x = factor(.data[[cluster_col]]), y = proportion, fill = factor(.data[[cluster_col]]))) +
 #     geom_col(color = "white", alpha = 0.85) +
 #     geom_text(aes(label = scales::percent(proportion, accuracy = 0.1)), vjust = -0.5, size = 3.5) +
 #     coord_cartesian(ylim = c(0, y_max * 1.1)) +
 #     scale_fill_viridis_d(option = "D") +
 #     labs(
 #       title = paste0(label_name, " Cluster Proportions (", analysis_type, ") — ", y),
 #       x = paste0(label_name, " Cluster"), y = "Proportion of Households", fill = paste0(label_name, " Cluster")
 #     ) +
 #     theme_minimal(base_size = 12) +
 #     theme(legend.position = "none")
 # 
 #   print(p_year)
 # 
 #   ggsave(
 #     file.path(save_dir, paste0(label_name, "_", tolower(analysis_type), "_proportions_", y, ".png")),
 #     p_year, width = 7, height = 5, dpi = 30
 #   )
 # }

# # -------------------------------------------------------------------
# # 3. Animated bar plot — cycles through years
# # -------------------------------------------------------------------

# p_anim = ggplot(cluster_props, aes(x = factor(.data[[cluster_col]]), y = proportion, fill = factor(.data[[cluster_col]]))) +
#    geom_col(color = "white", alpha = 0.85) +
#    geom_text(aes(label = scales::percent(proportion, accuracy = 0.1)), vjust = -0.5, size = 4) +
#    coord_cartesian(ylim = c(0, y_max * 1.1)) +
#    scale_fill_viridis_d(option = "D") +
#    labs(
#      title = paste0(label_name, " Cluster Proportions (", analysis_type, ") — Year: {closest_state}"),
#      x = paste0(label_name, " Cluster"), y = "Proportion of Households", fill = paste0(label_name, " Cluster")
#    ) +
#    theme_minimal(base_size = 13) +
#    theme(legend.position = "none") +
#    transition_states(.data[[year_col]], transition_length = 2, state_length = 1) +
#    ease_aes("cubic-in-out")
# 
#  anim = animate(
#    p_anim,
#    nframes = 27,
#    fps = 3,
#    width = 800, height = 600,
#    renderer = gifski_renderer()
#  )
# 
#  anim_save(
#    file.path(save_dir, paste0(label_name, "_", tolower(analysis_type), "_proportions_animated.gif")),
#    animation = anim
#  )
# 
# anim
```

### Stats for Proportions Confirming the Significance of Changing Clusters Over Time

A two proportion test was conducted to investigate the year by year trends for each cluster to determine their significance.

Cluster 0 shows multiple statistically significant decline scattered throughout the time span. There are no significant reversals of this trend, so this cluster demonstrates slow, step-wise decline.

Cluster 1 stayed stable. It had few significant shifts and the overall proportion of its diet ownership suggests it has no strong directional trend.

Cluster 2 starts tiny and continuously grows to end with a diet proportion of 40%. It is the most dynamic cluster with string of statistically significant upward changes. It can confidently be said there is a significant strong positive trend in in its dietary proportion represented in households.

Cluster 3 fluctuates around 25-28%, it has volatility in 1990s, but beyond these outliers, it remains generally stable with fewer significant year to year changes.

Cluster 4 has the largest initial share of diet. It consistently has downward trends, when disregarding the shock during 1990-1992. It has a sustained statistically significant downward trend over the time period.

```{r}
data_source = qual_pca_nute    # your dataset
cluster_col = "cluster"        # categorical cluster membership (0:4)
year_col    = "styr"
label_name  = "nute"           # used in output labeling/filenames

##save_dir = "output_plots"
#dir.create(save_dir, showWarnings = FALSE, recursive = TRUE)

# -------------------------------------------------------------------
# 1. Prep data — counts and proportions per cluster per year
# -------------------------------------------------------------------

cluster_data = data_source %>%
  select(hhno, all_of(year_col), all_of(cluster_col)) %>%
  filter(!is.na(.data[[cluster_col]]))

cluster_props = cluster_data %>%
  group_by(.data[[year_col]], .data[[cluster_col]]) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(.data[[year_col]]) %>%
  mutate(total = sum(n), proportion = n / total) %>%
  ungroup() %>%
  arrange(.data[[cluster_col]], .data[[year_col]])

# print(kable(cluster_props, digits = 4))

clusters = sort(unique(cluster_props[[cluster_col]]))
years    = sort(unique(cluster_props[[year_col]]))

#Consecutive year-over-year proportion tests, PER CLUSTER
#(two-proportion z-test: is cluster K's share different between year A and year B?)

pairwise_results = list()

for (clust in clusters) {
  for (i in 2:length(years)) {

    yr_prev = years[i - 1]
    yr_curr = years[i]

    row_prev = cluster_props %>% filter(.data[[year_col]] == yr_prev, .data[[cluster_col]] == clust)
    row_curr = cluster_props %>% filter(.data[[year_col]] == yr_curr, .data[[cluster_col]] == clust)

     #Skip if cluster didn't appear at all in one of the two years
    if (nrow(row_prev) == 0 || nrow(row_curr) == 0) next

    n_success = c(row_prev$n, row_curr$n)
   n_total   = c(row_prev$total, row_curr$total)

    ptest = prop.test(n_success, n_total)

    pairwise_results[[paste0(clust, "_", yr_prev, "_vs_", yr_curr)]] = tibble(
      cluster        = clust,
      year_prev      = yr_prev,
      year_curr      = yr_curr,
      prop_prev      = row_prev$proportion,
      prop_curr      = row_curr$proportion,
      prop_change    = row_curr$proportion - row_prev$proportion,
      chi_sq         = unname(ptest$statistic),
      p_value        = ptest$p.value,
      significant    = ifelse(ptest$p.value < 0.05, "Yes", "No")
    )}}

pairwise_table = bind_rows(pairwise_results) %>% arrange(cluster, year_prev)

#| label: tbl-cluster-change-summary
#| tbl-cap: "Significance of year-by-year changes, by cluster"

cluster_change_summary = cluster_props %>%
  group_by(.data[[cluster_col]]) %>%
  summarise(n_years_present = n_distinct(.data[[year_col]]), .groups = "drop") %>%
  rename(cluster = !!cluster_col) %>%
  left_join(
    pairwise_table %>%
      group_by(cluster) %>%
      summarise(
        n_transitions_tested = n(),
        n_significant        = sum(significant == "Yes"),
        .groups = "drop"
      ),
    by = "cluster"
  ) %>%
  mutate(pct_significant = percent(n_significant / n_transitions_tested, accuracy = 0.1)) %>%
  arrange(cluster) %>%
  select(cluster, n_years_present, n_transitions_tested, n_significant, pct_significant)

kable(
  cluster_change_summary,
  col.names = c("Cluster", "Years Present", "Year-to-Year Transitions Tested",
                "# Significant Transitions", "% of Year ChangesSignificant"),
  align = "c",
  caption = "Significance of year-by-year changes, by nutrient cluster"
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  column_spec(4, bold = TRUE)


```

### Cochran-Armitage Test

The Cochran-Armitage trend test was applied separately to each of the five clusters, testing whether that cluster's share of the population trended consistently upward or downward across the ordered sequence of survey years (1974-2000). It binary checked if the change in households was significantly different between the initial and final years to mark long-term trends. It found that all but cluster 1 experience significant change during the time frame. The confirms the listed trends, focusing on cluster 2 are not defined by noise in the data.Together, these results indicate a substantial compositional shift in the population's cluster membership over the 27-year period, with Cluster 2 gaining population share at the expense of Clusters 0, 3, and 4, while Cluster 1 remained a stable, low-prevalence group throughout.

```{r}
#| label: tbl-cochran-armitage
#| tbl-cap: "Cochran-Armitage trend test results, by nutrient cluster"

# Trend test across ALL years, PER CLUSTER
# (Cochran-Armitage: is there a consistent up/down trend in this cluster's
#  share across the full time span?)

trend_results = list()

for (clust in clusters) {

  clust_data = cluster_props %>% filter(.data[[cluster_col]] == clust) %>% arrange(.data[[year_col]])

  if (nrow(clust_data) < 3) next  # trend test needs several time points

  trend_test = prop.trend.test(clust_data$n, clust_data$total)

  trend_results[[as.character(clust)]] = tibble(
    cluster       = clust,
    n_years       = nrow(clust_data),
    first_year    = min(clust_data[[year_col]]),
    last_year     = max(clust_data[[year_col]]),
    prop_first    = clust_data$proportion[which.min(clust_data[[year_col]])],
    prop_last     = clust_data$proportion[which.max(clust_data[[year_col]])],
    chi_sq        = unname(trend_test$statistic),
    p_value       = trend_test$p.value,
    significant_trend = ifelse(trend_test$p.value < 0.05, "Yes", "No")
  )
}

trend_table = bind_rows(trend_results)

kable(
  trend_table %>%
    mutate(
      prop_first = percent(prop_first, accuracy = 0.1),
      prop_last  = percent(prop_last, accuracy = 0.1),
      p_value    = pvalue(p_value, accuracy = 0.001, add_p = TRUE),
      chi_sq     = round(chi_sq, 2)
    ) %>%
    select(cluster, n_years, first_year, last_year, prop_first, prop_last, chi_sq, p_value, significant_trend),
  col.names = c("Cluster", "# Years", "First Year", "Last Year",
                "Proportion (First Year)", "Proportion (Last Year)",
                "Chi-sq Statistic", "p-value", "Significant Trend?"),
  align = "c",
  caption = "Cochran-Armitage trend test results, by nutrient cluster"
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  row_spec(which(trend_table$significant_trend == "Yes"), bold = TRUE, background = "#eaf7ea") %>%
  column_spec(9, bold = TRUE)

# Multinomial model: cluster membership ~ year

#model_data = data_source %>%
 # select(hhno, all_of(year_col), all_of(cluster_col)) %>%
 # filter(!is.na(.data[[cluster_col]])) %>%
 # mutate(
  #  cluster_fct = relevel(factor(.data[[cluster_col]]), ref = "0"),  # set reference cluster
  #  year_num = as.numeric(.data[[year_col]]))

# Fit model: does year predict cluster membership?
#mod_full = multinom(cluster_fct ~ year_num, data = model_data, trace = FALSE)
#mod_null = multinom(cluster_fct ~ 1, data = model_data, trace = FALSE)

# Likelihood ratio test: is year a significant predictor overall?
#lr_test = anova(mod_null, mod_full)
#print(lr_test)

# Per-cluster coefficients: direction/magnitude of each cluster's trend
# relative to the reference cluster (cluster 0)
#tidy(mod_full, conf.int = TRUE) %>%
  #filter(term == "year_num") %>%
  #select(y.level, estimate, std.error, conf.low, conf.high, p.value) %>%
  #print()
```

### Companion Robustness: Kendall Tau Trend Test

```{r}
#| label: tbl-kendall-tau
#| tbl-cap: "Kendall's tau rank-correlation trend test, by nutrient cluster"

kendall_results = list()

for (clust in clusters) {
  clust_series = cluster_props %>% filter(.data[[cluster_col]] == clust) %>% arrange(.data[[year_col]])
  if (nrow(clust_series) < 3) next

  k_test = suppressWarnings(cor.test(clust_series[[year_col]], clust_series$proportion, method = "kendall"))

  kendall_results[[as.character(clust)]] = tibble(
    cluster     = clust,
    tau         = unname(k_test$estimate),
    p_value     = k_test$p.value,
    significant = ifelse(k_test$p.value < 0.05, "Yes", "No")
  )
}

kendall_table = bind_rows(kendall_results)

kable(
  kendall_table %>%
    mutate(tau = round(tau, 3), p_value = pvalue(p_value, accuracy = 0.001, add_p = TRUE)),
  col.names = c("Cluster", "Kendall's tau", "p-value", "Significant Trend?"),
  align = "c",
  caption = "Kendall's tau rank-correlation trend test, by nutrient cluster"
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  row_spec(which(kendall_table$significant == "Yes"), bold = TRUE, background = "#eaf7ea")
```